(Working Title) Properties of the \KT\ Campaign 1 Planets, False Positive Probabilities, and Confirmation of $N$ Systems. You Were Warned: it's a Working Title.

### 2015-02-27 ms.tex
Archival imaging words, but not data or figures.

This is Ben.

>>>>

For the stars with AO nondetections, there is still the
possibility that a background binary could be positioned
directly behind the target star, evading detection.
The probability is small, given the $0\farcs1$ diffraction limit
of P200 at $2\mu$m, but nonzero.
We can rule out the possibility of such chance alignments with 
archival imaging data.

\btmtodo{Method}

\btmtodo{Plots showing POSS observations.}

For these targets, we can extend our contrast curves to zero 
present-day orbital separation and rule out the possibility that
these transit events are caused by background eclipsing binaries.
By combining present-day seeing-limited photometric survey data, 
adaptive optics imaging, and archival photometry, the only stellar companions 
we would not detect would be those that are gravitationally bound to the target 
star and positioned in their orbits so that their projected separation is
smaller than the diffraction limit of the P200 telescope.
Such an alignment would require the orbital inclination of the binary to be 
nearly $90^\circ$ and the phase $\varpi + \theta \approx \pi/2$ or $3\pi/2$.
While we cannot fully rule out this possibility, such an alignment is unlikely
to occur, and highly unlikely to cause enough dilution to call the planetary
nature of these signals into question.
